---
title: "Historic potato yield WA"
author: "El Nazarov"
date: "9/16/2020"
output: html_document
---
#### Resource: https://docs.ropensci.org/rnassqs/  
##### Load libraries.  
```{r message=FALSE, warning=FALSE}
library(rnassqs) # For harvest yield data
library(pkgmaker)
library(dplyr)
library(ggplot2)
library(data.table)
```  
##### Set API key. 
API key: 603EE21B-9682-3233-8C15-260C6E388A51
```{r}
nassqs_auth(key = '603EE21B-9682-3233-8C15-260C6E388A51')
# need to conceal API key?
```
##### Define search parameters.
```{r setup, include=FALSE}
nassqs_params()
```
##### Define search parameters: potato yield data from Washington state
#### Sanity check: Gather potato data for year 1950 in Washington
```{r}
params <- list(commodity_desc = "potatoes", year = 1950, state_alpha = "WA")

nassqs(params)
```
## Yield
```{r}
nassqs_yields(params) 
```
### Collect data from multiple years
## Define new dataframe of potato yield data in WA
```{r}
param_list <- list(commodity_desc = "potatoes", state_alpha = "WA")
```
### Acreage, iterate through each year to get data
```{r}
data_list <- lapply(1882:2019, function(yr) {
  params <- param_list
  params[['year']] <- yr
  nassqs_yields(params)
})
```
#### Using dplyr to bind the data list
```{r}
dta <- rbindlist(data_list, use.names = TRUE)
```
### Inspect data structure and features
#### Check that our record request is under the 50,000 limit
```{r setup, include=FALSE}
dim(dta) 
table(dta$year)
str(dta)
```
### Summary statistics
```{r setup, include=FALSE}
class(dta$Value)
dta$Value
```
### Coerce value into a number
```{r setup, include=FALSE, warning=F}
dta$value <- as.numeric(gsub(",", "", dta$Value))
dta$value
summary(as.numeric(dta$value))
lapply(dta, unique)
```
### Plot
#### Set plot size
```{r}
options(repr.plot.width = 20, repr.plot.height = 10)
```
#### Create plot
```{r}
dta %>%
  group_by(year) %>%
  select(year, Value, county_name) %>%
  ggplot(aes(x=year, y=Value)) +
  geom_jitter(aes(colour = county_name), size=5, alpha=3/5) +
  theme_classic() +
  theme(axis.title.x=element_text(size=16, face="bold"),
        axis.text.x=element_text(size=14),
        axis.title.y=element_text(size=16,face="bold"),
        axis.text.y=element_text(size=14)) +
  scale_color_hue(l=70, c=40) +
  labs(x="Time (1882-2019)",
       y="Yield") +
  geom_smooth(method = "loess", span = 0.1, se = FALSE, color="grey40")
```
## Map Data
### Install and load packages
```{r}
library(cartography)
library(sf)
```

#### Map of Washington with counties
```{r}
wa_geojson <- "https://opendata.arcgis.com/datasets/12712f465fc44fb58328c6e0255ca27e_11.geojson"
wa_count_raw <- sf::read_sf(wa_geojson)
plot(st_geometry(wa_count_raw))
```
##Sanity check: map feature data
```{r}
head(wa_count_raw)
```
###Clean geospatial dataframe
```{r}
wa_counties <- wa_count_raw %>% 
  dplyr::transmute(
    OBJECTID,
    MAP_NAME = JURISDICT_LABEL_NM, 
    COUNTY = toupper(JURISDICT_LABEL_NM) 
    )
```



















####Boneyard
```{r}

```