---
title: "Historic potato yield WA"
author: "El Nazarov"
date: "9/16/2020"
output: html_document
---


###Load libraries
``` {r}
library(tidyverse)
library(data.table)
```

###Read in crop yeild file
```{r}
dta <- read_csv("/Users/elman/Documents/GitHub/PotatoAcerageAndYields/WA_potato_yield_revised.csv")
view(dta)
```

###Inspect data 
```{r}
str(dta) #structure
```

```{r}
table(dta$Year) #number of entries per year
```

###Summary statistics
```{r}
class(dta$Value) #checking class of value
```

```{r}
duplicates_dta <-duplicated(dta) #determine if duplicate data is detected
isTRUE(duplicates_dta)
```

```{r}
summary(dta$Value) #summaries of the yield values
```

```{r}
lapply(dta, unique) #observe unique elements?
```

###Plot data
```{r}
# Plot size
options(repr.plot.width = 20, repr.plot.height = 10)
# Plot
dta %>%
group_by(Year) %>%
select(Year, Value, County) %>%
ggplot(aes(x=Year, y=Value)) +
geom_jitter(aes(colour = County), size=1, alpha=3/5) +
theme_classic() + 
theme(axis.title.x=element_text(size=16, face="bold"),
      axis.text.x=element_text(size=14),
      axis.title.y=element_text(size=16,face="bold"),
      axis.text.y=element_text(size=14)) +
scale_color_hue(l=70, c=40) +
labs(x="Time (1965-2015)",
    y="Acres")  +
geom_smooth(method = "loess", span = 0.1, se = FALSE, color="grey40")
```
## Washington counties mapping

### Load packages
```{r, message=F, echo=F}
# Packages for graphics
library(ggplot2)
library(gridExtra)
library(ggExtra)
library(naniar) # To visualize missing data
library(Hmisc) # To tabulate a summary of the data
library(maps) # for maps
library(knitr) # format tables
library(ggplot2) # For diagnostics
# Packages for data wrangling
library(dplyr)
library(tidyr)
library(reshape2)
# Packages for inference /presentation of inference*
library(stargazer)
library(plm) # For estimating fixed and random effect model
library(lmtest)
library(sandwich) # for robust standard errors
library(knitr)
opts_chunk$set(tidy.opts=list(width.cutoff=60),tidy=TRUE)
```

### Load historic potato acreage data
```{r}
dta #Load in yeild

df <- dta #Rename dataframe

```

### Summary of dataframe
```{r}

str(df) #Checking structure 

summary(df) #Summary of dataframe

```

### Check for missing values
```{r}
is.na(df)
```
### Open map data
```{r message=F, warning=F, fig.cap="Potato yield in Washington state over time", echo=FALSE}
MainStates <- map_data("state")
```

# Average yeild of WA counties over time
```{r}
# Automate county level average for each county
MuYeildDf <- df %>%
  group_by(County) %>%
  summarise('MuYeild' = mean(Value, na.rm = TRUE)) %>%
  dplyr::select(MuYeild, County) 
```


```{r}
MuYeildDf[nrow(MuYeildDf) + 1,] = list(0, "garfield")
#Delete first row in MuAcreageDf that is blank in the county row and the average of all the counties in the other row and remove Other(combined)counties row
MuYeildDf <- MuYeildDf[-c(1,25),]
#Rename county column in MuAcreageDf to "subregion" to match the map county column name and change the MuYeildDf counties to all lowercase to match the map dataframe so they can be joined
colnames(MuYeildDf)[2] <- "subregion"
MuYeildDf$subregion <- tolower(MuYeildDf$subregion)
#Round MuYeild to a whole number
MuYeildDf[,-2] <- round(MuYeildDf[,-2],0)
# Coerce Value to numeric
as.numeric(as.character(dta$Value))
class(dta)
#dta[county_name == "COLUMBIA",] # what does (D) mean?- Not enough farms to enable anonymity (pg.X in doc Y)
```


### WA county map
```{r}
# Base WA county map
states <- map_data("state")
dim(states)
wa_df <- subset(states, region == "washington")
head(wa_df)
counties <- map_data("county")
wa_county <- subset(counties, region == "washington")
head(wa_county)
wa_base <- ggplot(data = wa_df,
                  mapping = aes(x = long,
                                y = lat,
                                group = 
group,
fill = subregion)) +
coord_fixed(1.3) +
geom_polygon(color = "black", fill = "gray")
wa_base + theme_classic() +
geom_polygon(data = wa_county, fill = NA, color = "white") +
geom_polygon(color = "black", fill = NA)  # get the state border back on top
#Joined county data, wa_county dataframe is map data for the counties in Washington state, MuAcreageDf includes the average potato acreage for each county over time
JoinedCounties <- inner_join(wa_county, MuYeildDf, by = "subregion")
# WA county map with joined data. Color gradient based on MuYeild column
MuYeildPlot <- ggplot() + 
  geom_polygon(data=JoinedCounties ,
               aes(x=long, y=lat, group=group,
               fill=MuYeild),
                color="black", lwd=0.3) +
  scale_fill_gradient(low="blue", high="red") +
  theme_classic() + coord_map("conic", lat0 = 30) +
  ggtitle("WA County Historic Potato Yeild Averages 1965-2015")
#Add surrounding states and provinces to WA map
us <- getData("GADM",country="USA",level=1)
canada <- getData("GADM",country="CAN",level=1)
states <- c('Idaho', 'Oregon')
provinces <- c("British Columbia", "Alberta")
# PNW
us.states <- us[us$NAME_1 %in% states,]
# Canada
ca.provinces <- canada[canada$NAME_1 %in% provinces,]
#WA average map with surrounding states and provinces
PNWAcreage <- ggplot(us.states,
       aes(x=long, y=lat, group=group))+
  geom_path(size=0.25)+
  geom_path(data=ca.provinces, size=0.25,color="grey60")+
  geom_polygon(data=subset(us.states, NAME_1 %in% c('Idaho', 'Oregon')),
               aes(x=long, y=lat, group=group), fill="white", colour = "grey50", size=0.50)+ 
 geom_polygon(data=JoinedCounties, #Start of MuAcreagePlot
               aes(x=long, y=lat, group=group,
               fill=MuAcres),
                color="black", lwd=0.3) +
  scale_fill_gradient(low="blue", high="red") +
  theme_classic() + coord_map("conic", lat0 = 30) +
  ggtitle("WA County Historic Potato Acreage Averages 1882-2019") + 
  labs(fill = "Average Acreage")+
  labs(caption = "Counties shown in grey were not included in NASS dataset to protect farm anonymity.") +
  theme(plot.caption = element_text(hjust = 0))+ #End of MuAcreagePlot
  theme(panel.background = element_rect(fill = "white", colour = "grey50"))+
 coord_map("bonne", lat0 = 50,
            xlim = c(-127, -112),ylim = c(41, 50))+
  xlab("Longitude") +
  ylab("Latitude") 
```
```{r}
# Reading in potato acreage data from NASS from 1965-2015 and selecting year, county and value (acreage)
ShortHistoricAcreageCSV <- read.csv(file = 'HistoricPotatoData.csv')
ShortHistoricAcreage <- dplyr::select(ShortHistoricAcreageCSV, "County", "Year", "Value") 
# Delete rows that are for combined counties
ShortHistoricAcreage <- ShortHistoricAcreage[!grepl("COMBINED",ShortHistoricAcreage$County),]
#Coerce Value column from character to numeric
ShortHistoricAcreage$Value = as.numeric(gsub(",", "", ShortHistoricAcreage$Value))
ShortHistoricAcreage$Value
summary(as.numeric(ShortHistoricAcreage$Value))
lapply(ShortHistoricAcreage, unique)
#Rename county column in ShortHistoricAcreage to "subregion" to match the map county column name and change the ShortHistoricAcreage counties to all lowercase to match the map dataframe so they can be joined
colnames(ShortHistoricAcreage)[1] <- "subregion"
ShortHistoricAcreage$subregion <- tolower(ShortHistoricAcreage$subregion) 
#Spreading data, making long data wide so we can make an acreage map for each year
SpreadAcreage <- spread(ShortHistoricAcreage, Year,Value)
#Converting NA to 0 (For counties included in the data set for years when they did not report any acreage, we will consider that 0 acreages.)
SpreadAcreage[is.na(SpreadAcreage)] <- 0
# Adding counties not included in the NASS data set so they will be included on the map, but without any acreage associated with them: Asotin, Chelan, Clallam, Columbia, Ferry, Garfield, Jefferson, Mason, Pacific, Pend Oreille, San Juan, Skamania, Wahkiakum. A single year with NA listed so the rows will add correctly (dummy variable) 
SpreadAcreage[nrow(SpreadAcreage) + 1,] = ("asotin")
SpreadAcreage[nrow(SpreadAcreage) + 1,] = ("chelan")
SpreadAcreage[nrow(SpreadAcreage) + 1,] = ("clallam")
SpreadAcreage[nrow(SpreadAcreage) + 1,] = ("columbia")
SpreadAcreage[nrow(SpreadAcreage) + 1,] = ("ferry")
SpreadAcreage[nrow(SpreadAcreage) + 1,] = ("garfield")
SpreadAcreage[nrow(SpreadAcreage) + 1,] = ("jefferson")
SpreadAcreage[nrow(SpreadAcreage) + 1,] = ("mason")
SpreadAcreage[nrow(SpreadAcreage) + 1,] = ("pacific")
SpreadAcreage[nrow(SpreadAcreage) + 1,] = ("pend oreille")
SpreadAcreage[nrow(SpreadAcreage) + 1,] = ("san juan")
SpreadAcreage[nrow(SpreadAcreage) + 1,] = ("skamania")
SpreadAcreage[nrow(SpreadAcreage) + 1,] = ("wahkiakum")
#Converting acreage columns (columns 2:50) to numeric
num_cols <- c(2:50)
SpreadAcreage[,num_cols] <- lapply(SpreadAcreage[,num_cols] , as.numeric)
#Joined county data, wa_county dataframe is map data for the counties in Washington state, SpreadAcreage includes the  potato acreage for each county over time
JoinedSpreadCounties <- inner_join(wa_county, SpreadAcreage, by = "subregion")
# Renamed column names for the year data so they can be used to fill the color gradient for the maps 
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1965 = 7)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1966 = 8)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1967 = 9)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1968 = 10)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1969 = 11)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1970 = 12)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1971 = 13)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1972 = 14)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1973 = 15)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1974 = 16)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1975 = 17)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1976 = 18)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1977 = 19)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1978 = 20)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1979 = 21)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1980 = 22)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1981 = 23)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1982 = 24)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1983 = 25)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1984 = 26)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1985 = 27)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1986 = 28)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1987 = 29)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1988 = 30)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1989 = 31)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1990 = 32)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1991 = 33)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1992 = 34)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1993 = 35)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1994 = 36)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1995 = 37)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1996 = 38)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1997 = 39)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1998 = 40)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1999 = 41)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage2000 = 42)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage2001 = 43)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage2002 = 44)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage2003 = 45)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage2004 = 46)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage2005 = 47)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage2006 = 48)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage2007 = 49)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage2008 =50)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage2009 = 51)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage2010 = 52)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage2011 = 53)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage2012 = 54)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage2014 = 55) 
# WA county map with joined data. Color gradient based on 1965 data column
Acreage1965 <- ggplot() + 
  geom_polygon(data=JoinedSpreadCounties ,
               aes(x=long, y=lat, group=group,
               fill=Acreage1965),
                color="black", lwd=0.3) +
  scale_fill_gradient(low="blue", high="red") +
  theme_classic() + coord_map("conic", lat0 = 30) +
  ggtitle("WA County Potato Acreage 1965")
#Add surrounding states and provinces to WA map
us <- getData("GADM",country="USA",level=1)
canada <- getData("GADM",country="CAN",level=1)
states <- c('Idaho', 'Oregon', 'California', 'Utah', 'Montana', 'Nevada', 'Wyoming')
provinces <- c("British Columbia", "Alberta")
# PNW
us.states <- us[us$NAME_1 %in% states,]
# Canada
ca.provinces <- canada[canada$NAME_1 %in% provinces,]
#WA 1965 map with surrounding states and provinces
PNWAcreage1965 <- ggplot(us.states,
       aes(x=long, y=lat, group=group))+
  geom_path(size=0.25)+
  geom_path(data=ca.provinces, size=0.25,color="grey60")+
  geom_polygon(data=subset(us.states, NAME_1 %in% c('Idaho', 'Oregon', 'California', 'Utah', 'Montana', 'Nevada', 'Wyoming' )),
               aes(x=long, y=lat, group=group), fill="white", colour = "grey50", size=0.50)+ 
 geom_polygon(data=JoinedSpreadCounties ,
               aes(x=long, y=lat, group=group,
               fill=Acreage1965),
                color="black", lwd=0.3, alpha=0.7) +
  scale_fill_gradient(low="blue", high="red") +
  theme_classic() + coord_map("conic", lat0 = 30) +
  ggtitle("WA County Potato Acreage 1965") + 
  labs(fill = "Acreage")+
  labs(caption = "Counties shown in grey were not included in the NASS data set.") +
  theme(plot.caption = element_text(hjust = 0))+ 
  theme(panel.background = element_rect(fill = "white", colour = "grey50"))+
 coord_map("bonne", lat0 = 50,
            xlim = c(-125, -116),ylim = c(45, 50))+
  xlab("Longitude") +
  ylab("Latitude")
  
  
#Looping map plots
acreage_cols <- c(7:55)
plot=list(seq(length(acreage_cols)))
for (c in seq_along(acreage_cols)){
  plot[[c]]=ggplotggplot(us.states,
       aes(x=long, y=lat, group=group))+
  geom_path(size=0.25)+
  geom_path(data=ca.provinces, size=0.25,color="grey60")+
  geom_polygon(data=subset(us.states, NAME_1 %in% c('Idaho', 'Oregon', 'California', 'Utah', 'Montana', 'Nevada', 'Wyoming' )),
               aes(x=long, y=lat, group=group), fill="white", colour = "grey50", size=0.50)+ 
 geom_polygon(data=JoinedSpreadCounties ,
               aes(x=long, y=lat, group=group,
               fill=acreage_cols),
                color="black", lwd=0.3, alpha=0.8) +
  scale_fill_gradient(low="blue", high="red") +
  theme_classic() + coord_map("conic", lat0 = 30) +
  ggtitle("WA County Potato Acreage") + 
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(fill = "Acreage")+
  labs(caption = "Counties shown in grey were not included in the NASS data set.") +
  theme(plot.caption = element_text(hjust = 0.5))+ 
  theme(panel.background = element_rect(fill = "white", colour = "grey50"))+
 coord_map("bonne", lat0 = 50,
            xlim = c(-125, -114),ylim = c(42, 50))+
  xlab("Longitude") +
  ylab("Latitude") 
}
#Arrange plots
do.call(grid.arrange, 
        c(plot, nrow=48, ncol=1,
          top=("WA County Potato Acreage"),
          left=("Year")))
 ```
 
### Graveyard
- This code chunk does XYZ
-This code gives a county map of WA, not using ggplot plot_usmap(regions = "counties", include = c("WA"))
- Good example on how to color-code based on value ranges: 
 scale_color_manual(name = "value",
                     values = c("(-Inf,10]" = "red",
                                  "(10,100]" = "yellow",
                                  "(100, Inf]" = "black"),
                     labels = c("Acreage <= 10", "10 < Acreage <= 100", "Acreage > 100"))
```{r}
dta %>%
  dplyr::select('AverageAcerage' = mean(acerage)) # package::function()
 ``` 
# Outlier plot

```{r}
dta %>%
  group_by(year) %>%
  select(year, value, county_name) %>%
  ggplot(aes(x=year, y=value)) +
  geom_point(aes(colour = cut(value, c(-Inf, 10, 100, Inf))),
             size = 1)+
  scale_color_manual(name = "value",
                     values = c("(-Inf,10]" = "red",
                                  "(10,100]" = "yellow",
                                  "(100, Inf]" = "black"),
                     labels = c("Acreage <= 10", "10 < Acreage <= 100", "Acreage > 100")) +
  theme_classic() +
  theme(axis.title.x=element_text(size=16, face="bold"),
        axis.text.x=element_text(size=14),
        axis.title.y=element_text(size=16,face="bold"),
        axis.text.y=element_text(size=14)) +
  labs(x="Time (1882-2019)",
       y="Acres") +
  ggtitle("WA County Historic Potato Acreages") +
  theme(plot.title = element_text(hjust = 0.5)) +
  geom_smooth(method = "loess", span = 0.1, se = FALSE, color="grey40")+
  theme(legend.position = "right")  
### Average acreage per county, counties with single digit acreages have notes
# Adams
AdamsData <- subset(dta, county_name == 'ADAMS') 
AdamsAverageAcreage <- mean(AdamsData$value, na.rm = TRUE)
# Asotin
AsotinData <- subset(dta, county_name == 'ASOTIN')
AsotinAverageAcreage <- mean(AsotinData$value, na.rm = TRUE)
### Asotin only has 1 acre listed for 2 years of recorded data?
# Benton
BentonData <- subset(dta, county_name == 'BENTON')
BentonAverageAcreage <- mean(BentonData$value, na.rm = TRUE)
# Chelan
ChelanData <- subset(dta, county_name == 'CHELAN')
ChelanAverageAcreage <- mean(ChelanData$value, na.rm = TRUE)
### Weird values too, only 1 or 2 acres listed
# Clallam
ClallamData <- subset(dta, county_name == 'CLALLAM')
ClallamAverageAcreage <- mean(ClallamData$value, na.rm = TRUE)
### Weird low acreages 
# Clark
ClarkData <- subset(dta, county_name == 'CLARK')
ClarkAverageAcreage <- mean(ClarkData$value, na.rm = TRUE)
# Columbia
ColumbiaData <- subset(dta, county_name == 'COLUMBIA')
ColumbiaAverageAcreage <- mean(ColumbiaData$value, na.rm = TRUE)
### All values N/A or listed as "D"
# Cowlitz
CowlitzData<- subset(dta, county_name == 'COWLITZ')
CowlitzAverageAcreage <- mean(CowlitzData$value, na.rm = TRUE)
# Douglas
DouglasData <- subset(dta, county_name == 'DOUGLAS')
DouglasAverageAcreage <- mean(DouglasData$value, na.rm = TRUE)
# Ferry
FerryData <- subset(dta, county_name == 'FERRY')
FerryAverageAcreage <- mean(FerryData$value, na.rm = TRUE)
### Only 1 acre listed
# Franklin
FranklinData <- subset(dta, county_name == 'FRANKLIN')
FranklinAverageAcreage <- mean(FranklinData$value, na.rm = TRUE)
# Garfield, none
GarfieldAverageAcreage <- 0
# Grant
GrantData <- subset(dta, county_name == 'GRANT')
GrantAverageAcreage <- mean(GrantData$value, na.rm = TRUE)
# Grays Harbor
GraysHarborData <- subset(dta, county_name == 'GRAYS HARBOR')
GraysHarborAverageAcreage <- mean(GraysHarborData$value, na.rm = TRUE)
# Island
IslandData <- subset(dta, county_name == 'ISLAND')
IslandAverageAcreage <- mean(IslandData$value, na.rm = TRUE)
# Jefferson
JeffersonData <- subset(dta, county_name == 'JEFFERSON')
JeffersonAverageAcreage <- mean(JeffersonData$value, na.rm = TRUE)
### Low acreage
# King
KingData <- subset(dta, county_name == 'KING')
KingAverageAcreage <- mean(KingData$value, na.rm = TRUE)
# Kitsap
KitsapData <- subset(dta, county_name == 'KITSAP')
KitsapAverageAcreage <- mean(KitsapData$value, na.rm = TRUE)
### Low acreage
# Kittitas
KittitasData <- subset(dta, county_name == 'KITTITAS')
KittitasAverageAcreage <- mean(KittitasData$value, na.rm = TRUE)
# Klickitat
KlickitatData <- subset(dta, county_name == 'KLICKITAT')
KlickitatAverageAcreage <- mean(KlickitatData$value, na.rm = TRUE)
# Lewis
LewisData <- subset(dta, county_name == 'LEWIS')
LewisAverageAcreage <- mean(LewisData$value, na.rm = TRUE)
### Low acreage
# Lincoln
LincolnData <- subset(dta, county_name == 'LINCOLN')
LincolnAverageAcreage <- mean(LincolnData$value, na.rm = TRUE)
# Mason
MasonData <- subset(dta, county_name == 'MASON')
MasonAverageAcreage <- mean(MasonData$value, na.rm = TRUE)
### Low acreage
# Okanogan
OkanoganData <- subset(dta, county_name == 'OKANOGAN')
OkanoganAverageAcreage <- mean(OkanoganData$value, na.rm = TRUE)
# Pacific
PacificData <- subset(dta, county_name == 'PACIFIC')
PacificAverageAcreage <- mean(PacificData$value, na.rm = TRUE)
### Low acreage
# Pend Oreille
PendOreilleData <- subset(dta, county_name == 'PEND OREILLE')
PendOreilleAverageAcreage <- mean(PendOreilleData$value, na.rm = TRUE)
### Low acreage
# Pierce
PierceData <- subset(dta, county_name == 'PIERCE')
PierceAverageAcreage <- mean(PierceData$value, na.rm = TRUE)
# San Juan
SanJuanData <- subset(dta, county_name == 'SAN JUAN')
SanJuanAverageAcreage <- mean(SanJuanData$value, na.rm = TRUE)
### Low acreage
# Skagit
SkagitData <- subset(dta, county_name == 'SKAGIT')
SkagitAverageAcreage <- mean(SkagitData$value, na.rm = TRUE)
# Skamania
SkamaniaData <- subset(dta, county_name == 'SKAMANIA')
SkamaniaAverageAcreage <- mean(SkamaniaData$value, na.rm = TRUE)
### Low acreage
# Snohomish
SnohomishData<- subset(dta, county_name == 'SNOHOMISH')
SnohomishAverageAcreage <- mean(SnohomishData$value, na.rm = TRUE)
# Spokane
SpokaneData <- subset(dta, county_name == 'SPOKANE')
SpokaneAverageAcreage <- mean(SpokaneData$value, na.rm = TRUE)
# Stevens
StevensData <- subset(dta, county_name == 'STEVENS')
StevensAverageAcreage <- mean(StevensData$value, na.rm = TRUE)
# Thurston
ThurstonData <- subset(dta, county_name == 'THURSTON')
ThurstonAverageAcreage <- mean(ThurstonData$value, na.rm = TRUE)
### Low acreage
# Wahkiakum
WahkiakumData <- subset(dta, county_name == 'WAHKIAKUM')
WahkiakumAverageAcreage <- mean(WahkiakumData$value, na.rm = TRUE)
### Low acreage
# Walla Walla
WallaWallaData <- subset(dta, county_name == 'WALLA WALLA')
WallaWallaAverageAcreage <- mean(WallaWallaData$value, na.rm = TRUE)
# Whatcom
WhatcomData <- subset(dta, county_name == 'WHATCOM')
WhatcomAverageAcreage <- mean(WhatcomData$value, na.rm = TRUE)
# Whitman
WhitmanData <- subset(dta, county_name == 'WHITMAN')
WhitmanAverageAcreage <- mean(WhitmanData$value, na.rm = TRUE)
# Yakima
YakimaData<- subset(dta, county_name == 'YAKIMA')
YakimaAverageAcreage <- mean(YakimaData$value, na.rm = TRUE)
# Other/unlisted
OtherUnlistedData <- subset(dta, county_name == '')
OtherUnlistedAverageAcreage <- mean(OtherUnlistedData$value, na.rm = TRUE)
### Dataframe of means
WACountyMeans <- data.frame(AdamsAverageAcreageele, AsotinAverageAcreage, BentonAverageAcreage, ChelanAverageAcreage, ClallamAverageAcreage, ClarkAverageAcreage, ColumbiaAverageAcreage, CowlitzAverageAcreage, DouglasAverageAcreage, FerryAverageAcreage, FranklinAverageAcreage, GarfieldAverageAcreage, GrantAverageAcreage, GraysHarborAverageAcreage, IslandAverageAcreage, JeffersonAverageAcreage, KingAverageAcreage, KitsapAverageAcreage, KittitasAverageAcreage, KlickitatAverageAcreage, LewisAverageAcreage, LincolnAverageAcreage, MasonAverageAcreage, OkanoganAverageAcreage, PacificAverageAcreage, PendOreilleAverageAcreage, PierceAverageAcreage, SanJuanAverageAcreage, SkagitAverageAcreage, SkamaniaAverageAcreage, SnohomishAverageAcreage, SpokaneAverageAcreage, StevensAverageAcreage, ThurstonAverageAcreage, WahkiakumAverageAcreage, WallaWallaAverageAcreage, WhatcomAverageAcreage, WhitmanAverageAcreage, YakimaAverageAcreage, OtherUnlistedAverageAcreage)
#How to use aggregate example:
  #Subset county data
WACountyData <- aggregate(dta[, "value"],
                          by = list(dta$county_name),
                          FUN = mean,
                          na.rm = TRUE,
                          data = dta) 
```
```{r}
#Extracted county acreages
AcreageWithoutCounties <- subset(HistoricAcreage, county_name == '')
AdamsHistoricAcreage <- AdamsData %>%
  dplyr::select("county_name", "year", "value")
AsotinHistoricAcreage <- AsotinData %>%
  dplyr::select("county_name", "year", "value")
BentonHistoricAcreage <- BentonData %>%
  dplyr::select("county_name", "year", "value")
ChelanHistoricAcreage <- ChelanData %>%
  dplyr::select("county_name", "year", "value")
ClallamHistoricAcreage <- ClallamData %>%
  dplyr::select("county_name", "year", "value")
ClarkHistoricAcreage <- ClarkData %>%
  dplyr::select("county_name", "year", "value")
ColumbiaHistoricAcreage <- ColumbiaData %>%
  dplyr::select("county_name", "year", "value")
CowlitzHistoricAcreage <- CowlitzData %>%
  dplyr::select("county_name", "year", "value")
DouglasHistoricAcreage <- DouglasData %>%
  dplyr::select("county_name", "year", "value")
FerryHistoricAcreage <- FerryData %>%
  dplyr::select("county_name", "year", "value")
FranklinHistoricAcreage <- FranklinData %>%
  dplyr::select("county_name", "year", "value")
GrantHistoricAcreage <- GrantData %>%
  dplyr::select("county_name", "year", "value")
GraysHarborHistoricAcreage <- GraysHarborData %>%
  dplyr::select("county_name", "year","value")
IslandHistoricAcreage <- IslandData %>%
  dplyr::select("county_name", "year", "value")
JeffersonHistoricAcreage <- JeffersonData %>%
  dplyr::select("county_name", "year", "value")
KingHistoricAcreage <- KingData %>%
  dplyr::select("county_name", "year", "value")
KitsapHistoricAcreage <- KitsapData %>%
  dplyr::select("county_name", "year", "value")
KittitasHistoricAcreage <- KittitasData %>%
  dplyr::select("county_name", "year", "value")
KlickitatHistoricAcreage <- KlickitatData %>%
  dplyr::select("county_name", "year", "value")
LewisHistoricAcreage <- LewisData %>%
  dplyr::select("county_name", "year", "value")
LincolnHistoricAcreage <- LincolnData %>%
  dplyr::select("county_name", "year", "value")
MasonHistoricAcreage <- MasonData %>%
  dplyr::select("county_name", "year", "value")
OkanoganHistoricAcreage <- OkanoganData %>%
  dplyr::select("county_name", "year", "value")
PacificHistoricAcreage <- PacificData %>%
  dplyr::select("county_name", "year", "value")
PendOreilleHistoricAcreage <- PendOreilleData %>%
  dplyr::select("county_name", "year", "value")
PierceHistoricAcreage <- PierceData %>%
  dplyr::select("county_name", "year", "value")
SanJuanHistoricAcreage <- SanJuanData %>%
  dplyr::select("county_name", "year", "value")
SkagitHistoricAcreage <- SkagitData %>%
  dplyr::select("county_name", "year", "value")
SkamaniaHistoricAcreage <- SkamaniaData %>%
  dplyr::select("county_name", "year", "value")
SnohomishHistoricAcreage <- SnohomishData %>%
  dplyr::select("county_name", "year", "value")
SpokaneHistoricAcreage <- SpokaneData %>%
  dplyr::select("county_name", "year", "value")
StevensHistoricAcreage <- StevensData %>%
  dplyr::select("county_name", "year", "value")
ThurstonHistoricAcreage <- ThurstonData %>%
  dplyr::select("county_name", "year", "value")
WahkiakumHistoricAcreage <- WahkiakumData %>%
  dplyr::select("county_name", "year", "value")
WallaWallaHistoricAcreage <- WallaWallaData %>%
  dplyr::select("county_name", "year", "value")
WhatcomHistoricAcreage <- WhatcomData %>%
  dplyr::select("county_name", "year", "value")
WhitmanHistoricAcreage <- WhitmanData %>%
  dplyr::select("county_name", "year", "value")
YakimaHistoricAcreage <- YakimaData %>%
  dplyr::select("county_name", "year", "value")
```
```{r}
#Gathered yearly acreage data
##Create new dataframe that only includes the county, year and acreage (value), columns from the original dta dataframe
HistoricAcreage <- dta %>%
  dplyr::select(county_name, year, value) #Many instances of years with acreage values but no county listed. Sometimes the same year has more than one acreage listed. Sometimes these repeated years have the same acreage, sometimes it is different.
#Still need help on this
GatheredData <- gather(HistoricAcreage, year, value, -county_name)
# This is long data, does it need to be wide? Issue with converting from long to wide with spread(), I think due to each county sometimes having the same year listed more than once (examples show show things like counties associated with only one year.)
```


```{r}
# For loop gather for mapping multiple individual years of data
## Notes: Collect an acreage point for each county for each year available. Have all the points for a single year plotted onto the county map. Use same color gradient as average acreage plot. Gather and for loops can automate this process for each year.
## Sample of a few years, hardcoded just to see what we're working with
Data1882 <- dta%>%
  subset(year==1882) #No specific counties listed
Data2019 <- dta %>%
  subset(year==2019)#No specific counties listed
Data2017 <- dta %>% 
  subset(year==2017) #Multiple acreages listed for the same county (same county, same year, different acreages, may just be different regions within the county). Check sector_desc, domain_desc, util_practice_desc, short_desc
```








Boneyard:
```{r}
tolower(colnames(dta)) #make column names lower case
str(dta)
```