---
title: "Historic potato yield WA"
author: "El Nazarov"
date: "9/16/2020"
output: html_document
---
#### Resource: https://docs.ropensci.org/rnassqs/  
##### Load libraries.  
```{r message=FALSE, warning=FALSE}
library(rnassqs) # For harvest yield data
library(pkgmaker)
library(dplyr)
library(ggplot2)
library(data.table)
```  
##### Set API key. 
API key: 603EE21B-9682-3233-8C15-260C6E388A51
```{r}
nassqs_auth(key = '603EE21B-9682-3233-8C15-260C6E388A51')
# need to conceal API key?
```
##### Define search parameters.
```{r setup, include=FALSE}
nassqs_params()
```
##### Define search parameters: potato yield data from Washington state
#### Sanity check: Gather potato data for year 1950 in Washington
```{r}
params <- list(commodity_desc = "potatoes", year = 1950, state_alpha = "WA")

nassqs(params)
```
## Yield
```{r}
nassqs_yields(params) 
```
### Collect data from multiple years
## Define new dataframe of potato yield data in WA
```{r}
param_list <- list(commodity_desc = "potatoes", state_alpha = "WA")
```
### Acreage, iterate through each year to get data
```{r}
data_list <- lapply(1882:2019, function(yr) {
  params <- param_list
  params[['year']] <- yr
  nassqs_yields(params)
})
```
#### Using dplyr to bind the data list
```{r}
dta <- rbindlist(data_list, use.names = TRUE)
```
### Inspect data structure and features
#### Check that our record request is under the 50,000 limit
```{r setup, include=FALSE}
dim(dta) 
table(dta$year)
str(dta)
```
### Summary statistics
```{r setup, include=FALSE}
class(dta$Value)
dta$Value
```
### Coerce value into a number
```{r setup, include=FALSE, warning=F}
dta$value <- as.numeric(gsub(",", "", dta$Value))
dta$value
summary(as.numeric(dta$value))
lapply(dta, unique)
```
### Plot
#### Set plot size
```{r}
options(repr.plot.width = 20, repr.plot.height = 10)
```
#### Create plot
```{r}
dta %>%
  group_by(year) %>%
  select(year, value, county_name) %>%
  ggplot(aes(x=year, y=value)) +
  geom_jitter(aes(colour = county_name), size=5, alpha=3/5) +
  theme_classic() +
  theme(axis.title.x=element_text(size=16, face="bold"),
        axis.text.x=element_text(size=14),
        axis.title.y=element_text(size=16,face="bold"),
        axis.text.y=element_text(size=14)) +
  scale_color_hue(l=70, c=40) +
  labs(x="Time (1882-2019)",
       y="Yield") +
  geom_smooth(method = "loess", span = 0.1, se = FALSE, color="grey40")
```
## Map Data
### Install and load packages
```{r}
library("rnaturalearth")
library("rnaturalearthdata")
library("ggplot2")
library("rworldmap")
library(dplyr)
library(geosphere)
library(gpclib)
library(tidyverse)
library(mapdata)
library(raster)
library(geojsonio)
library(usmap)
```
## World Map
#### Map of US with several states outlined as a trial/practice map
```{r}
worldMap <- getMap()
world.points <- fortify(worldMap)
world.points$region <- world.points$id
states <- map_data("state")
states = states %>%
  filter(region %in% c("montana", "california","washington","pennsylvania"))#

world.df <- world.points[,c("long","lat","group", "region")]

p = worldmap <- ggplot() + 
  geom_polygon(data = world.df, aes(x = long, y = lat, group = group),
               color="grey", fill="grey") +
  geom_polygon(data = states, aes(x = long, y = lat, group = group),
               color="black", fill="grey", lwd=0.35) +
  scale_y_continuous(breaks = (-2:2) * 30) +
  scale_x_continuous(breaks = (-4:4) * 45) +
  coord_map("ortho", orientation=c(40, -90, 0))

```






######This is old code. 
--------------------------------------------------------------------------------
```{r}
yield_df <- nassqs_yields(params) #define the data frame to a variable
```
## From here, a narrower selection of data can begin (sanity check). 
```{r}
str(yield_df) #find desired parameters within data frame
```
#### Sanity check: confirm that the desired time frame was collected. And establish time frame from which data will be collected.
```{r}
plot(table(yield_df$year)) #This shows that there is at least 1 entry for each year the data is available, 1882-2019.
```
#### Select/subset desired parameters/columns.  
Choose from options listed in the structure.
```{r}
yield <- yield_df %>% select(Value, 
                             commodity_desc, 
                             county_name,
                             year, 
                             state_alpha,
                             unit_desc,
                             statisticcat_desc) 
```
#### Sanity check: determine class of the value. clean up the new data frame.
```{r}
class(yield$Value)
```
### Sanity check
```{r}
head(yield$Value) #Head will show only the first 5 entries.
```
### Coerce "Value" vector from character to number.
```{r}
yield$ValueInteger = as.integer(yield$Value) 
# Sanity check
head(yield)
plot(yield$value, yield$ValueInteger) # error x and y differ in lengths
```
#### Summary
```{r}
summary(yield$value)
```
#### Plot
```{r}
options(repr.plot.width = 20, repr.plot.height = 10) # Plot size

yield %>%
group_by(year) %>%
select(year, value, county_name) %>%
ggplot(aes(x=year, y=value)) +
geom_jitter(aes(colour = county_name), size=5, alpha=3/5) +
theme_classic() + 
theme(axis.title.x=element_text(size=16, face="bold"),
      axis.text.x=element_text(size=14),
      axis.title.y=element_text(size=16,face="bold"),
      axis.text.y=element_text(size=14)) +
scale_color_hue(l=70, c=40) +
labs(x="Time (1882-2019)",
    y="Yield (CWT/acre)")  +
geom_smooth(method = "loess", span = 0.1, se = FALSE, color="grey40")
```

####Boneyard
```{r}

```