---
title: "Historic potato acreage WA"
author: "Hannah Tarlyn"
date: "9/19/2020"
output: html_document
---
### Load libraries
```{r}
library(rnassqs)
library(pkgmaker)
library(dplyr)
library(ggplot2)
library(data.table)
```
### Set API key
```{r}
nassqs_auth(key = 'E41D0CC0-8353-3153-A16A-850F2F13AC0E')
```

### Define search parameters
```{r setup, include=FALSE}
nassqs_params()
```
#### Parameters to query on the data call
#### Gather potato data for year 1950 in Washington
```{r}
params <- list(commodity_desc = "potatoes", year = 1950, state_alpha = "WA")

nassqs(params)
```
# Acreage
```{r}
nassqs_acres(params)
```
### Collect data from multiple years
#### Define the list of parameters to use repeatedly
```{r}
param_list <- list(commodity_desc = "potatoes", state_alpha = "WA")
```
### Acreage, iterate through each year to get data
```{r}
data_list <- lapply(1882:2019, function(yr) {
  params <- param_list
  params[['year']] <- yr
  nassqs_acres(params)
})
```
#### Using dplyr to bind the data list
```{r}
dta <- rbindlist(data_list, use.names = TRUE)
```
### Inspect data structure and features
#### Check that our record request is under the 50,000 limit
```{r, results='hide'}
dim(dta)
table(dta$year)
str(dta)
```
### Summary statistics
```{r setup, include=FALSE}
class(dta$Value)
dta$Value
```
### Coerce value into a number
```{r}
dta$value = as.numeric(gsub(",", "", dta$Value))
dta$value
summary(as.numeric(dta$value))
lapply(dta, unique)
```
### Plot
#### Set plot size
```{r}
options(repr.plot.width = 20, repr.plot.height = 10)
```
#### Create plot
```{r}
dta %>%
  group_by(year) %>%
  select(year, value, county_name) %>%
  ggplot(aes(x=year, y=value)) +
  geom_jitter(aes(colour = county_name), size=5, alpha=3/5) +
  theme_classic() +
  theme(axis.title.x=element_text(size=16, face="bold"),
        axis.text.x=element_text(size=14),
        axis.title.y=element_text(size=16,face="bold"),
        axis.text.y=element_text(size=14)) +
  scale_color_hue(l=70, c=40) +
  labs(x="Time (1882-2019)",
       y="Acres") +
  geom_smooth(method = "loess", span = 0.1, se = FALSE, color="grey40")
```

## Map Data
### Install and load packages
```{r}
library("rnaturalearth")
library("rnaturalearthdata")
library("ggplot2")
library("rworldmap")
library(dplyr)
library(geosphere)
library(gpclib)
library(tidyverse)
library(mapdata)
library(raster)
library(geojsonio)
library(usmap)
```
## World Map
#### Map of US with several states outlined as a trial/practice map
```{r}
worldMap <- getMap()
world.points <- fortify(worldMap)
world.points$region <- world.points$id
states <- map_data("state")
states = states %>%
  filter(region %in% c("montana", "california","washington","pennsylvania"))#

world.df <- world.points[,c("long","lat","group", "region")]

p = worldmap <- ggplot() + 
  geom_polygon(data = world.df, aes(x = long, y = lat, group = group),
               color="grey", fill="grey") +
  geom_polygon(data = states, aes(x = long, y = lat, group = group),
               color="black", fill="grey", lwd=0.35) +
  scale_y_continuous(breaks = (-2:2) * 30) +
  scale_x_continuous(breaks = (-4:4) * 45) +
  coord_map("ortho", orientation=c(40, -90, 0))

p

##setwd('/Users/Hannah 23/Documents')
# Saving the map as a tiff file
tiff('PA.tiff', units="in", 
     width=5, height=5,
     res=600, compression = 'lzw')
p
dev.off()
```

## PNW
### Obtain data, states and provinces in and around PNW
```{r}
us <- getData("GADM",country="USA",level=1)
canada <- getData("GADM",country="CAN",level=1)
states <- c('Idaho', 'Oregon', 'Washington', 'Montana', 'California', 'Nevada', 'Utah', 'Wyoming')
provinces <- c("British Columbia", "Alberta")
```
### Subset data into US states and Canadian provinces
```{r}
us.states <- us[us$NAME_1 %in% states,]
ca.provinces  <- canada[canada$NAME_1 %in% provinces,]
```
### Plot of PNW with states of interest outlined in black and surrounding states in grey
```{r}
p <- ggplot(us.states,
       aes(x=long, y=lat, group=group))+
  geom_path(size=0.25)+
  geom_path(data=ca.provinces, size=0.25,color="grey60")+
  geom_path(data=subset(us.states, NAME_1 %in% c('Montana', 'California','Nevada','Utah','Wyoming')),
            size=0.25,color="grey60")+
  geom_polygon(data=subset(us.states, NAME_1 %in% c('Idaho', 'Oregon', 'Washington')),
               aes(x=long, y=lat, group=group), fill="white", colour = "black", size=0.50)+
  theme(panel.background = element_rect(fill = "white", colour = "grey50"))+
  coord_map("bonne", lat0 = 50,
            xlim = c(-127, -112),ylim = c(41, 50))+
  xlab("Longitude") +
  ylab("Latitude")
  
```

```{r}
####setwd('/Users/Hannah 23/Documents')
#### Changing plot size and saving as a tiff file


tiff('PNW-s.tiff', units="in", 
     width=10, height=10,
     res=300, compression = 'lzw')
options(repr.plot.width=20, repr.plot.height=20)
p
dev.off()
```

## Washington counties mapping

### Load packages
```{r, message=F, echo=F}
# Packages for graphics
library(ggplot2)
library(gridExtra)
library(ggExtra)
library(naniar) # To visualize missing data
library(Hmisc) # To tabulate a summary of the data
library(maps) # for maps
library(knitr) # format tables
library(ggplot2) # For diagnostics
# Packages for data wrangling
library(dplyr)
library(tidyr)
library(reshape2)
# Packages for inference /presentation of inference*
library(stargazer)
library(plm) # For estimating fixed and random effect model
library(lmtest)
library(sandwich) # for robust standard errors
library(knitr)
opts_chunk$set(tidy.opts=list(width.cutoff=60),tidy=TRUE)
```
### Load historic potato acreage data
```{r setup, include=FALSE}
data_list #Load in acreage
#Rename dataframe
df <- data_list
```
### Summary of dataframe
```{r}
#Checking structure 
str(df)
#Summary of dataframe
summary("df")

```
### Check for missing values
```{r}
is.na(x)
```
### Open map data
```{r message=F, warning=F, fig.cap="Potato acreage in Washington state over time", echo=FALSE}
MainStates <- map_data("state")

### Add new columns for potato acerage over time, subset of dta dataframe. Select columns for value (acreage), state_name (Washington), year and county_name. (Check back:Mutate to create new column called region.There are 2913 rows of data.)

Statesdf <- dta[ , c("value", "state_name", "year", "county_name")]%>%
  mutate("region" = rep(unique(MainStates$region)[2913],
                       each=1))

### Plot acreage(value) by year, need add color. Log(value)?

ggplot(Statesdf, aes(x=year, y=value)) +
  geom_line() + geom_point(size=0.05, alpha=0.5) +
  facet_wrap(~region) + 
  theme_classic() +
  theme(legend.position="none",
      axis.text.y=element_text(size=4),
      axis.text.x=element_text(size=4, angle = 90))
```
### WA county map plotting as histogram
```{r message=F, warning=F, fig.cap="A: Histogram of potato acreage in Washington state over time. Each color represents a different county. B: Distribution of acreage", echo=FALSE}
State.Mu.TF <- Statesdf %>%
  group_by(region) %>%
  summarise(TF.mu=mean(value))
### Rename region column
names(State.Mu.TF)[1] <- "region"
### Join acreage data with map data
JoinedStates <- inner_join(MainStates, 
                           State.Mu.TF,
                           by = "region")
### Plots
A <- ggplot() + 
  geom_polygon(data=JoinedStates ,
               aes(x=long, y=lat, group=group,
               fill=TF.mu),
                color="black", lwd=0.3) +
  scale_fill_gradient(low="blue", high="red") +
  theme_classic() + coord_map("conic", lat0 = 30) + 
  labs(title="A",fill=expression("Potato acreage in Washington state over time"),size=2) +
  theme(axis.line=element_blank(),
        axis.text.x=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks=element_blank(),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        legend.position="right",
        panel.background=element_blank(),
        panel.border=element_blank(),
        panel.grid.major=element_blank(),
        panel.grid.minor=element_blank(),
        plot.background=element_blank())+
  theme(legend.title=element_text(size=5))

B <- ggplot(Statesdf, aes(x=factor(year), y=value),
        group=year) +
  geom_boxplot(color="grey60", outlier.colour = "grey60") +
  geom_jitter(alpha=0.4,color="grey60",
              position=position_jitter(width=0.1)) +
  geom_smooth(method = "loess", se=F, 
              aes(group=1), span=0.1, color="orangered", alpha=0.7) +
  labs(title="B", y=expression("Potato acreage in Washington state over time"), x="Time (1882-2019)") +
  theme_classic() + 
  theme(legend.position="none",
        axis.title.y=element_text(size=8),
        axis.text.x = element_text(angle = 90))
B<-ggMarginal(B, type="histogram",
           margins = "y",
           col="gray",
           fill = "grey83")
           
grid.arrange(A,B)
```
### Average acreage per county, counties with single digit acreages have notes
```{r}
# Adams
AdamsData <- subset(dta, county_name == 'ADAMS') 
AdamsAverageAcreage <- mean(AdamsData$value, na.rm = TRUE)

# Asotin
AsotinData <- subset(dta, county_name == 'ASOTIN')
AsotinAverageAcreage <- mean(AsotinData$value, na.rm = TRUE)
### Asotin only has 1 acre listed for 2 years of recorded data?

# Benton
BentonData <- subset(dta, county_name == 'BENTON')
BentonAverageAcreage <- mean(BentonData$value, na.rm = TRUE)

# Chelan
ChelanData <- subset(dta, county_name == 'CHELAN')
ChelanAverageAcreage <- mean(ChelanData$value, na.rm = TRUE)
### Weird values too, only 1 or 2 acres listed

# Clallam
ClallamData <- subset(dta, county_name == 'CLALLAM')
ClallamAverageAcreage <- mean(ClallamData$value, na.rm = TRUE)
### Weird low acreages 

# Clark
ClarkData <- subset(dta, county_name == 'CLARK')
ClarkAverageAcreage <- mean(ClarkData$value, na.rm = TRUE)

# Columbia
ColumbiaData <- subset(dta, county_name == 'COLUMBIA')
ColumbiaAverageAcreage <- mean(ColumbiaData$value, na.rm = TRUE)
### All values N/A or listed as "D"

# Cowlitz
CowlitzData<- subset(dta, county_name == 'COWLITZ')
CowlitzAverageAcreage <- mean(CowlitzData$value, na.rm = TRUE)

# Douglas
DouglasData <- subset(dta, county_name == 'DOUGLAS')
DouglasAverageAcreage <- mean(DouglasData$value, na.rm = TRUE)

# Ferry
FerryData <- subset(dta, county_name == 'FERRY')
FerryAverageAcreage <- mean(FerryData$value, na.rm = TRUE)
### Only 1 acre listed

# Franklin
FranklinData <- subset(dta, county_name == 'FRANKLIN')
FranklinAverageAcreage <- mean(FranklinData$value, na.rm = TRUE)

# Garfield, none
GarfieldAverageAcreage <- 0

# Grant
GrantData <- subset(dta, county_name == 'GRANT')
GrantAverageAcreage <- mean(GrantData$value, na.rm = TRUE)

# Grays Harbor
GraysHarborData <- subset(dta, county_name == 'GRAYS HARBOR')
GraysHarborAverageAcreage <- mean(GraysHarborData$value, na.rm = TRUE)

# Island
IslandData <- subset(dta, county_name == 'ISLAND')
IslandAverageAcreage <- mean(IslandData$value, na.rm = TRUE)

# Jefferson
JeffersonData <- subset(dta, county_name == 'JEFFERSON')
JeffersonAverageAcreage <- mean(JeffersonData$value, na.rm = TRUE)
### Low acreage

# King
KingData <- subset(dta, county_name == 'KING')
KingAverageAcreage <- mean(KingData$value, na.rm = TRUE)

# Kitsap
KitsapData <- subset(dta, county_name == 'KITSAP')
KitsapAverageAcreage <- mean(KitsapData$value, na.rm = TRUE)
### Low acreage

# Kittitas
KittitasData <- subset(dta, county_name == 'KITTITAS')
KittitasAverageAcreage <- mean(KittitasData$value, na.rm = TRUE)

# Klickitat
KlickitatData <- subset(dta, county_name == 'KLICKITAT')
KlickitatAverageAcreage <- mean(KlickitatData$value, na.rm = TRUE)

# Lewis
LewisData <- subset(dta, county_name == 'LEWIS')
LewisAverageAcreage <- mean(LewisData$value, na.rm = TRUE)
### Low acreage

# Lincoln
LincolnData <- subset(dta, county_name == 'LINCOLN')
LincolnAverageAcreage <- mean(LincolnData$value, na.rm = TRUE)

# Mason
MasonData <- subset(dta, county_name == 'MASON')
MasonAverageAcreage <- mean(MasonData$value, na.rm = TRUE)
### Low acreage

# Okanogan
OkanoganData <- subset(dta, county_name == 'OKANOGAN')
OkanoganAverageAcreage <- mean(OkanoganData$value, na.rm = TRUE)

# Pacific
PacificData <- subset(dta, county_name == 'PACIFIC')
PacificAverageAcreage <- mean(PacificData$value, na.rm = TRUE)
### Low acreage

# Pend Oreille
PendOreilleData <- subset(dta, county_name == 'PEND OREILLE')
PendOreilleAverageAcreage <- mean(PendOreilleData$value, na.rm = TRUE)
### Low acreage

# Pierce
PierceData <- subset(dta, county_name == 'PIERCE')
PierceAverageAcreage <- mean(PierceData$value, na.rm = TRUE)

# San Juan
SanJuanData <- subset(dta, county_name == 'SAN JUAN')
SanJuanAverageAcreage <- mean(SanJuanData$value, na.rm = TRUE)
### Low acreage

# Skagit
SkagitData <- subset(dta, county_name == 'SKAGIT')
SkagitAverageAcreage <- mean(SkagitData$value, na.rm = TRUE)

# Skamania
SkamaniaData <- subset(dta, county_name == 'SKAMANIA')
SkamaniaAverageAcreage <- mean(SkamaniaData$value, na.rm = TRUE)
### Low acreage

# Snohomish
SnohomishData<- subset(dta, county_name == 'SNOHOMISH')
SnohomishAverageAcreage <- mean(SnohomishData$value, na.rm = TRUE)

# Spokane
SpokaneData <- subset(dta, county_name == 'SPOKANE')
SpokaneAverageAcreage <- mean(SpokaneData$value, na.rm = TRUE)

# Stevens
StevensData <- subset(dta, county_name == 'STEVENS')
StevensAverageAcreage <- mean(StevensData$value, na.rm = TRUE)

# Thurston
ThurstonData <- subset(dta, county_name == 'THURSTON')
ThurstonAverageAcreage <- mean(ThurstonData$value, na.rm = TRUE)
### Low acreage

# Wahkiakum
WahkiakumData <- subset(dta, county_name == 'WAHKIAKUM')
WahkiakumAverageAcreage <- mean(WahkiakumData$value, na.rm = TRUE)
### Low acreage

# Walla Walla
WallaWallaData <- subset(dta, county_name == 'WALLA WALLA')
WallaWallaAverageAcreage <- mean(WallaWallaData$value, na.rm = TRUE)

# Whatcom
WhatcomData <- subset(dta, county_name == 'WHATCOM')
WhatcomAverageAcreage <- mean(WhatcomData$value, na.rm = TRUE)

# Whitman
WhitmanData <- subset(dta, county_name == 'WHITMAN')
WhitmanAverageAcreage <- mean(WhitmanData$value, na.rm = TRUE)

# Yakima
YakimaData<- subset(dta, county_name == 'YAKIMA')
YakimaAverageAcreage <- mean(YakimaData$value, na.rm = TRUE)

# Other/unlisted
OtherUnlistedData <- subset(dta, county_name == '')
OtherUnlistedAverageAcreage <- mean(OtherUnlistedData$value, na.rm = TRUE)
```

```{r}
# Automate county level average for each county
MuAcreageDf <- dta %>%
  group_by(county_name) %>%
  summarise('MuAcres' = mean(dta$value, na.rm = TRUE)) %>%
  dplyr::select(MuAcres, county_name) 
#Subset county data
WACountyData <- aggregate(dta[, 40], list(dta$county_name), mean, na.rm = TRUE)
###Above is not matching the hard coded WACountyMeans data, some county means match, some don't, some that had values in WaCountyMeans are returning NaN in WaCountyData

#Need to manually add in Garfield county after Franklin county (not included on original dataframe, did not have any potato acreage listed)


#Delete first row in WaCountyData that is blank in the county row and the average of all the counties in the other row
WACountyData <- WACountyData[-c(1),]

#Rename county column in WACountyData to "subregion" to match the map county column name and change the WACountyData counties to all lowercase to match the map dataframe so they can be joined
colnames(WACountyData)[1] <- "subregion"

WACountyData = as.data.frame(sapply(WACountyData, tolower))

# Coerce Value to numeric
as.numeric(as.character(dta$Value))
class(dta)

dta[county_name == "COLUMBIA",] # what does (D) mean?- Not enough farms to enable anonymity (pg.X in doc Y)
```
### Dataframe of means
```{r}
WACountyMeans <- data.frame(AdamsAverageAcreage, AsotinAverageAcreage, BentonAverageAcreage, ChelanAverageAcreage, ClallamAverageAcreage, ClarkAverageAcreage, ColumbiaAverageAcreage, CowlitzAverageAcreage, DouglasAverageAcreage, FerryAverageAcreage, FranklinAverageAcreage, GrantAverageAcreage, GraysHarborAverageAcreage, IslandAverageAcreage, JeffersonAverageAcreage, KingAverageAcreage, KitsapAverageAcreage, KittitasAverageAcreage, KlickitatAverageAcreage, LewisAverageAcreage, LincolnAverageAcreage, MasonAverageAcreage, OkanoganAverageAcreage, PacificAverageAcreage, PendOreilleAverageAcreage, PierceAverageAcreage, SanJuanAverageAcreage, SkagitAverageAcreage, SkamaniaAverageAcreage, SnohomishAverageAcreage, SpokaneAverageAcreage, StevensAverageAcreage, ThurstonAverageAcreage, WahkiakumAverageAcreage, WallaWallaAverageAcreage, WhatcomAverageAcreage, WhitmanAverageAcreage, YakimaAverageAcreage, OtherUnlistedAverageAcreage)
```
### WA county map


```{r}
states <- map_data("state")
dim(states)
ut_df <- subset(states, region == "washington")
head(ut_df)

counties <- map_data("county")
ut_county <- subset(counties, region == "washington")
head(ut_county)

ut_base <- ggplot(data = ut_df, mapping = aes(x = long, y = lat, group = 
group)) +
coord_fixed(1.3) +
geom_polygon(color = "black", fill = "gray")

ut_base + theme_classic() +
geom_polygon(data = ut_county, fill = NA, color = "white") +
geom_polygon(color = "black", fill = NA)  # get the state border back on top
```


### Graveyard
- This code chunk does XYZ
-This code gives a county map of WA, not using ggplot plot_usmap(regions = "counties", include = c("WA"))
- Good example on how to color-code based on value ranges: 
 scale_color_manual(name = "value",
                     values = c("(-Inf,10]" = "red",
                                  "(10,100]" = "yellow",
                                  "(100, Inf]" = "black"),
                     labels = c("Acreage <= 10", "10 < Acreage <= 100", "Acreage > 100"))
```{r}
df %>%
  dplyr::select('AverageAcerage' = mean(acerage)) # package::function()
  ```
  # Outlier plot
  
```{r}
dta %>%
  group_by(year) %>%
  select(year, value, county_name) %>%
  ggplot(aes(x=year, y=value)) +
  geom_point(aes(colour = cut(value, c(-Inf, 10, 100, Inf))),
             size = 1)+
  scale_color_manual(name = "value",
                     values = c("(-Inf,10]" = "red",
                                  "(10,100]" = "yellow",
                                  "(100, Inf]" = "black"),
                     labels = c("Acreage <= 10", "10 < Acreage <= 100", "Acreage > 100")) +
  theme_classic() +
  theme(axis.title.x=element_text(size=16, face="bold"),
        axis.text.x=element_text(size=14),
        axis.title.y=element_text(size=16,face="bold"),
        axis.text.y=element_text(size=14)) +
  labs(x="Time (1882-2019)",
       y="Acres") +
  ggtitle("WA County Historic Potato Acreages") +
  theme(plot.title = element_text(hjust = 0.5)) +
  geom_smooth(method = "loess", span = 0.1, se = FALSE, color="grey40")+
  theme(legend.position = "right")  
```
