---
title: "Historic potato yield WA"
author: "El Nazarov"
date: "9/16/2020"
output: html_document
---


###Load libraries
``` {r}
library(tidyverse)
library(data.table)
library(pkgmaker)

```

###Read in crop yeild file
```{r}
dta <- read_csv("/Users/elman/Documents/GitHub/PotatoAcerageAndYields/WA_potato_yield_revised.csv")
view(dta)
```

###Inspect data 
```{r}
str(dta) #structure
```
```{r}
colnames(dta) <- tolower(colnames(dta)) #make column names lower case

str(dta)
```

####Inspect number of entries per year
```{r}
table(dta$year) #number of entries per year
```

###Summary statistics
```{r}
class(dta$value) #checking class of value
```

```{r}
summary(dta$value) #summaries of yield values
```

```{r}
duplicates_dta <-duplicated(dta) #determine if duplicate data is detected
isTRUE(duplicates_dta)
```
```{r}
lapply(dta, unique) #inspect unique values, find which counties are not included

#what to do with counties "other"?
```

###Plot data
```{r}
# Plot size
options(repr.plot.width = 20, repr.plot.height = 10)
# Plot
dta %>%
group_by(year) %>%
dplyr::select(year, value, county) %>%
ggplot(aes(x=year, y=value)) +
geom_jitter(aes(colour = county), size=1, alpha=3/5) +
theme_classic() + 
theme(axis.title.x=element_text(size=16, face="bold"),
      axis.text.x=element_text(size=14),
      axis.title.y=element_text(size=16,face="bold"),
      axis.text.y=element_text(size=14)) +
scale_color_hue(l=70, c=40) +
labs(x="Time (1965-2015)",
    y="Acres")  +
geom_smooth(method = "loess", span = 0.1, se = FALSE, color="grey40")
```
## Washington counties mapping

### Load packages
```{r, message=F, echo=F}
# Packages for graphics
library(ggplot2)
library(gridExtra)
library(ggExtra)
library(naniar) # To visualize missing data
library(Hmisc) # To tabulate a summary of the data
library(maps) # for maps
library(knitr) # format tables
library(ggplot2) # For diagnostics
# Packages for data wrangling
library(dplyr)
library(tidyr)
library(reshape2)
# Packages for inference /presentation of inference*
library(stargazer)
library(plm) # For estimating fixed and random effect model
library(lmtest)
library(sandwich) # for robust standard errors
library(knitr)
opts_chunk$set(tidy.opts=list(width.cutoff=60),tidy=TRUE)
library("rnaturalearth")
library("rnaturalearthdata")
library("ggplot2")
library("rworldmap")
library(dplyr)
library(geosphere)
library(gpclib)
library(tidyverse)
library(mapdata)
library(raster)
library(geojsonio)
library(usmap)

```

### Load historic potato acreage data
```{r}
dta #Load in yeild

df <- dta #Rename dataframe

```

### Summary of dataframe
```{r}

str(df) #Checking structure 

summary(df) #Summary of dataframe

```

### Check for missing values
```{r}
df_nas_value <- is.na(df$value)
sum(df_nas_value)
```
### Open map data
```{r message=F, warning=F, fig.cap="Potato acreage in Washington state over time", echo=FALSE}
MainStates <- map_data("state")
```

# Average yeild of WA counties over time
```{r}
# Automate county level average for each county
MuYieldDf <- df %>%
  group_by(county) %>%
  summarise('MuYield' = mean(value, na.rm = TRUE)) %>%
  dplyr::select(MuYield, county) #Need to manually add in counties named "Other", or not present in the data frame

str(MuYieldDf)
```
#Check which counties are missing data
```{r}
entries_yr_county <- table(df$year, df$county)

entries_yr_county
```
#Round MuYield to a whole number
```{r}
MuYieldDf <- MuYieldDf %>% 
  mutate_if(is.numeric, ~round(., 0))
View(MuYieldDf)
```

### WA county map
```{r}
# Base WA county map
states <- map_data("state")
dim(states)
wa_df <- subset(states, region == "washington")
head(wa_df)
counties <- map_data("county")
wa_county <- subset(counties, region == "washington")
head(wa_county)
wa_base <- ggplot(data = wa_df,
                  mapping = aes(x = long,
                                y = lat,
                                group = 
group,
fill = subregion)) +
coord_fixed(1.3) +
geom_polygon(color = "black", fill = "gray")
wa_base + theme_classic() +
geom_polygon(data = wa_county, fill = NA, color = "white") +
geom_polygon(color = "black", fill = NA)  # get the state border back on top
```

#Remove Other(combined)counties row
```{r}
MuYieldDf <- MuYieldDf[-c(17),]
```

#Rename county column in MuYieldDf to "subregion" to match the map county column name
```{r}
colnames(MuYieldDf)[2] <- "subregion"
```

```{r}
#Joined county data, wa_county dataframe is map data for the counties in Washington state, MuYieldDf includes the average potato yield for each county over time
JoinedCounties <- inner_join(wa_county, MuYieldDf, by = "subregion")
# WA county map with joined data. Color gradient based on MuYield column
MuYieldPlot <- ggplot() + 
  geom_polygon(data=JoinedCounties ,
               aes(x=long, y=lat, group=group,
               fill=MuYield),
                color="black", lwd=0.3) +
  scale_fill_gradient(low="blue", high="red") +
  theme_classic() + coord_map("conic", lat0 = 30) +
  ggtitle("WA County Historic Potato Yield Averages 1965-2015")

```

#Add surrounding states and provinces to WA map
```{r}
us <- getData("GADM", country="USA",level=1)
canada <- getData("GADM",country="CAN",level=1)
states <- c('Idaho', 'Oregon')
provinces <- c("British Columbia", "Alberta")
# PNW
us.states <- us[us$NAME_1 %in% states,]
# Canada
ca.provinces <- canada[canada$NAME_1 %in% provinces,]
#WA average map with surrounding states and provinces
PNWYield <- ggplot(us.states,
       aes(x=long, y=lat, group=group))+
  geom_path(size=0.25)+
  geom_path(data=ca.provinces, size=0.25,color="grey60")+
  geom_polygon(data=subset(us.states, NAME_1 %in% c('Idaho', 'Oregon')),
               aes(x=long, y=lat, group=group), fill="white", colour = "grey50", size=0.50)+ 
 geom_polygon(data=JoinedCounties, #Start of MuYieldPlot
               aes(x=long, y=lat, group=group,
               fill=MuYield),
                color="black", lwd=0.3) +
  scale_fill_gradient(low="blue", high="red") +
  theme_classic() + coord_map("conic", lat0 = 30) +
  ggtitle("WA County Historic Potato Yield Averages 1965-2015") + 
  labs(fill = "Average Yield")+
  labs(caption = "Counties shown in grey were not included in NASS dataset to protect farm anonymity.") +
  theme(plot.caption = element_text(hjust = 0))+ #End of MuYieldPlot
  theme(panel.background = element_rect(fill = "white", colour = "grey50"))+
 coord_map("bonne", lat0 = 50,
            xlim = c(-127, -112),ylim = c(41, 50))+
  xlab("Longitude") +
  ylab("Latitude") 


```
```{r}
# Adding counties not included in the NASS data set so they will be included on the map, but without any yield associated with them: Asotin, Chelan, Clallam, Columbia, Ferry, Garfield, Jefferson, Mason, Pacific, Pend Oreille, San Juan, Skamania, Wahkiakum. A single year with NA listed so the rows will add correctly (dummy variable) 
MuYieldDf[nrow(subregion) + 1,] = ("asotin")
MuYieldDf[nrow(MuYield) + 1,] = ("chelan")
MuYieldDf[nrow(MuYieldDf) + 1,] = ("clallam")
MuYieldDf[nrow(MuYieldDf) + 1,] = ("columbia")
MuYieldDf[nrow(MuYieldDf) + 1,] = ("ferry")
MuYieldDf[nrow(MuYieldDf) + 1,] = ("garfield")
MuYieldDf[nrow(MuYieldDf) + 1,] = ("jefferson")
MuYieldDf[nrow(MuYieldDf) + 1,] = ("mason")
MuYieldDf[nrow(MuYieldDf) + 1,] = ("pacific")
MuYieldDf[nrow(MuYieldDf) + 1,] = ("pend oreille")
MuYieldDf[nrow(MuYieldDf) + 1,] = ("san juan")
MuYieldDf[nrow(MuYieldDf) + 1,] = ("skamania")
MuYieldDf[nrow(MuYieldDf) + 1,] = ("wahkiakum")

```

```{r}
#Converting acreage columns (columns 2:50) to numeric
num_cols <- c(2:50)
SpreadAcreage[,num_cols] <- lapply(SpreadAcreage[,num_cols] , as.numeric)
#Joined county data, wa_county dataframe is map data for the counties in Washington state, SpreadAcreage includes the  potato acreage for each county over time
JoinedSpreadCounties <- inner_join(wa_county, SpreadAcreage, by = "subregion")
# Renamed column names for the year data so they can be used to fill the color gradient for the maps 
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1965 = 7)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1966 = 8)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1967 = 9)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1968 = 10)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1969 = 11)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1970 = 12)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1971 = 13)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1972 = 14)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1973 = 15)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1974 = 16)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1975 = 17)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1976 = 18)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1977 = 19)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1978 = 20)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1979 = 21)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1980 = 22)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1981 = 23)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1982 = 24)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1983 = 25)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1984 = 26)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1985 = 27)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1986 = 28)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1987 = 29)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1988 = 30)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1989 = 31)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1990 = 32)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1991 = 33)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1992 = 34)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1993 = 35)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1994 = 36)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1995 = 37)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1996 = 38)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1997 = 39)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1998 = 40)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage1999 = 41)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage2000 = 42)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage2001 = 43)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage2002 = 44)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage2003 = 45)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage2004 = 46)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage2005 = 47)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage2006 = 48)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage2007 = 49)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage2008 =50)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage2009 = 51)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage2010 = 52)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage2011 = 53)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage2012 = 54)
JoinedSpreadCounties <- JoinedSpreadCounties %>%
rename(Acreage2014 = 55) 
# WA county map with joined data. Color gradient based on 1965 data column
Acreage1965 <- ggplot() + 
  geom_polygon(data=JoinedSpreadCounties ,
               aes(x=long, y=lat, group=group,
               fill=Acreage1965),
                color="black", lwd=0.3) +
  scale_fill_gradient(low="blue", high="red") +
  theme_classic() + coord_map("conic", lat0 = 30) +
  ggtitle("WA County Potato Acreage 1965")
#Add surrounding states and provinces to WA map
us <- getData("GADM",country="USA",level=1)
canada <- getData("GADM",country="CAN",level=1)
states <- c('Idaho', 'Oregon', 'California', 'Utah', 'Montana', 'Nevada', 'Wyoming')
provinces <- c("British Columbia", "Alberta")
# PNW
us.states <- us[us$NAME_1 %in% states,]
# Canada
ca.provinces <- canada[canada$NAME_1 %in% provinces,]
#WA 1965 map with surrounding states and provinces
PNWAcreage1965 <- ggplot(us.states,
       aes(x=long, y=lat, group=group))+
  geom_path(size=0.25)+
  geom_path(data=ca.provinces, size=0.25,color="grey60")+
  geom_polygon(data=subset(us.states, NAME_1 %in% c('Idaho', 'Oregon', 'California', 'Utah', 'Montana', 'Nevada', 'Wyoming' )),
               aes(x=long, y=lat, group=group), fill="white", colour = "grey50", size=0.50)+ 
 geom_polygon(data=JoinedSpreadCounties ,
               aes(x=long, y=lat, group=group,
               fill=Acreage1965),
                color="black", lwd=0.3, alpha=0.7) +
  scale_fill_gradient(low="blue", high="red") +
  theme_classic() + coord_map("conic", lat0 = 30) +
  ggtitle("WA County Potato Acreage 1965") + 
  labs(fill = "Acreage")+
  labs(caption = "Counties shown in grey were not included in the NASS data set.") +
  theme(plot.caption = element_text(hjust = 0))+ 
  theme(panel.background = element_rect(fill = "white", colour = "grey50"))+
 coord_map("bonne", lat0 = 50,
            xlim = c(-125, -116),ylim = c(45, 50))+
  xlab("Longitude") +
  ylab("Latitude")
  
  
#Looping map plots
acreage_cols <- c(7:55)
plot=list(seq(length(acreage_cols)))
for (c in seq_along(acreage_cols)){
  plot[[c]]=ggplotggplot(us.states,
       aes(x=long, y=lat, group=group))+
  geom_path(size=0.25)+
  geom_path(data=ca.provinces, size=0.25,color="grey60")+
  geom_polygon(data=subset(us.states, NAME_1 %in% c('Idaho', 'Oregon', 'California', 'Utah', 'Montana', 'Nevada', 'Wyoming' )),
               aes(x=long, y=lat, group=group), fill="white", colour = "grey50", size=0.50)+ 
 geom_polygon(data=JoinedSpreadCounties ,
               aes(x=long, y=lat, group=group,
               fill=acreage_cols),
                color="black", lwd=0.3, alpha=0.8) +
  scale_fill_gradient(low="blue", high="red") +
  theme_classic() + coord_map("conic", lat0 = 30) +
  ggtitle("WA County Potato Acreage") + 
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(fill = "Acreage")+
  labs(caption = "Counties shown in grey were not included in the NASS data set.") +
  theme(plot.caption = element_text(hjust = 0.5))+ 
  theme(panel.background = element_rect(fill = "white", colour = "grey50"))+
 coord_map("bonne", lat0 = 50,
            xlim = c(-125, -114),ylim = c(42, 50))+
  xlab("Longitude") +
  ylab("Latitude") 
}
#Arrange plots
do.call(grid.arrange, 
        c(plot, nrow=48, ncol=1,
          top=("WA County Potato Acreage"),
          left=("Year")))
```
 



Boneyard:
```{r}
MuYieldDf[nrow(MuYeildDf) + 1,] = list(0, "garfield")
#Delete first row in MuYieldDf that is blank in the county row and the average of all the counties in the other row and remove Other(combined)counties row
MuYieldDf <- MuYieldDf[-c(1,25),]
#Rename county column in MuYieldDf to "subregion" to match the map county column name and change the MuYieldDf counties to all lowercase to match the map dataframe so they can be joined
colnames(MuAcreageDf)[2] <- "subregion"
MuAcreageDf$subregion <- tolower(MuAcreageDf$subregion)
```

```{r}
# Coerce Value to numeric
as.numeric(as.character(dta$value))
class(dta)
dta[county_name == "COLUMBIA",] # what does (D) mean?- Not enough farms to enable anonymity (pg.X in doc Y)
```

```{r}
# Reading in potato acreage data from NASS from 1965-2015 and selecting year, county and value (acreage)
ShortHistoricAcreageCSV <- read.csv(file = 'HistoricPotatoData.csv')
ShortHistoricAcreage <- dplyr::select(ShortHistoricAcreageCSV, "County", "Year", "Value") 
# Delete rows that are for combined counties
ShortHistoricAcreage <- ShortHistoricAcreage[!grepl("COMBINED",ShortHistoricAcreage$County),]
#Coerce Value column from character to numeric
ShortHistoricAcreage$Value = as.numeric(gsub(",", "", ShortHistoricAcreage$Value))
ShortHistoricAcreage$Value
summary(as.numeric(ShortHistoricAcreage$Value))
lapply(ShortHistoricAcreage, unique)
#Rename county column in ShortHistoricAcreage to "subregion" to match the map county column name and change the ShortHistoricAcreage counties to all lowercase to match the map dataframe so they can be joined
colnames(ShortHistoricAcreage)[1] <- "subregion"
ShortHistoricAcreage$subregion <- tolower(ShortHistoricAcreage$subregion) 
```

